Dependent Object Types

### 2012-09-05 doc/candidacy/slides.tex
a bit more tribalism

\begin{frame}{Tribe Calculus: Virtual Classes}
\begin{itemize}
\item {\it familes} of classes inherited together
\item classes are lexically nested inside other classes: when a class
  is inherited, its nested inner classes are inherited along with
  their methods and fields
\item two form of inheritance: subclassing and further binding
\item {\it family polymorphism}: code written for one family
  also works for extensions of that family
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Tribe Calculus: Virtual Classes}
\begin{itemize}
\item {\it familes} of classes inherited together
\item classes are lexically nested inside other classes: when a class
  is inherited, its nested inner classes are inherited along with
  their methods and fields
\item two form of inheritance: subclassing and further binding
\item {\it family polymorphism}: code written for one family
  also works for extensions of that family
\item in Tribe:\begin{itemize}
\item path types can depend simultaneously on both classes and objects
\item paths can use an {\tt out} field to move from an object to the
  object which surrounds it; enables ubiquitous access to an object's
  family without the need to drag around family arguments.
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Tribe: Example}
\begin{minted}{java}
class Graph {
  class Node {
    Edge connect(Node other) {
      return new Edge(this, other);
    }
  }
  class Edge {
    Node from, to;
    Edge(Node f, Node t) { from = f; to = t; }
  }
}

class ColouredGraph extends Graph { // subclassing
  class Node {                      // further binding
    Colour nodeColour;
  }
}
\end{minted}
\end{frame}

\begin{frame}[fragile]{Tribe: Example (continued)}
\begin{minted}{java}
final ColouredGraph cg1, cg2;
cg1.Node cn1, cn3;
cg2.Node cn2;
cn1.connect(cn3); // Type Correct
cn2.connect(cn3); // Type Error!!!

class Library {
  int distance(Graph.Node n1, n1.out.Node n2) { ... }

  e.out.Edge copyEdge(Graph.Edge e) {
    e.out.Node from = e.from;
    e.out.Node to = e.to;
    new e.out.Edge(from, to);
  }
}
\end{minted}
\end{frame}
